### 2014-03-02 paper/abstract.tex
Italics.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>
mashup
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{abstract}
    Many important security problems in JavaScript, including extension
    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
    XXX~\tocite{}, could be solved with a implementation
    of information flow control.  However, designing an IFC system which
    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
    we formally describe a coarse-grained IFC system which fulfills this
    criterion.  The key idea is that an efficient IFC system must not
    depend too much on the details of the language it is integrated
    with.  The result is a general method for adding IFC to existing
    languages which is indifferent to the choice of language.
    Additionally, we describe how to relate concrete implementations
    with the IFC systems produced by our technique and show how various
    proposed and existing IFC systems fit into our formal framework.
\end{abstract}

>>>>

\begin{abstract}
    Many important security problems in JavaScript, including extension
    security~\tocite{}, inclusion of untrusted libraries~\tocite{} and
    mash-up security~\tocite{}, could be solved with a implementation
    of information flow control.  However, designing an IFC system which
    can be \emph{efficiently} implemented is quite a challenge.  In this paper,
    we formally describe a coarse-grained IFC system which fulfills this
    criterion.  The key idea is that an efficient IFC system must not
    depend too much on the details of the language it is integrated
    with.  The result is a \emph{general} method for adding IFC to existing
    languages which is \emph{indifferent} to the choice of language.
    Additionally, we describe how to relate concrete implementations
    with the IFC systems produced by our technique and show how various
    proposed and existing IFC systems fit into our formal framework.
\end{abstract}
